Gradual Soundness: Lessons from Static Python

### 2022-05-17 pj-7.1/paper.tex
pj: reword gt comparison, remove contradiction

To be clear, gradual soundness has a different focus than gradual typing.
Gradual typing in the traditional, broad sense is about finding a best-of-both worlds
combination of typed and untyped
code~\cite{st-sfp-2006,tf-dls-2006,mf-toplas-2009,gktff-sfp-2006}.
Gradual soundness fits under this broad umbrella, and contributes the idea that multiple
type systems may be needed for an optimal mix.
Gradual typing in the refined sense calls for a dynamic type
that satisfies the gradual guarantees~\cite{svcb-snapl-2015}.
A gradually-sound language may choose to satisfy these guarantees.
\SP{}, however, does not~(\cref{s:type-dynamic}).

>>>>

Compared to traditional gradual typing, gradual soundness is a refinement.
The original gradual typing vision is to find a best-of-both-worlds combination
of typed and untyped code~\cite{st-sfp-2006,tf-dls-2006,mf-toplas-2009,gktff-sfp-2006}.
Gradual soundness fits under this broad umbrella, and contributes the idea that multiple
type systems may be needed for an optimal mix.
Gradual typing in the refined sense~\cite{svcb-snapl-2015} calls for a dynamic
type that satisfies the gradual guarantees.
A gradually-sound language may choose to satisfy these guarantees.
\SP{}, however, does not~(\cref{s:type-dynamic}).
